On Secure Delegation of SampBQP with a Classical Client

### 2020-02-01 bqp.tex
Make theorem stubs for BlindBQP

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Let $\lambda$ be the security parameter.
	Then \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}
\begin{proof}
	I promise this is true...
\end{proof}

@@

\begin{thm}
	compiles $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	into a $\QPIP_0$ protocol with negl. completeness and soundness
\end{thm}

>>>>

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

As we will see in the theorems below, \protoref{BlindBQP} is a $\QPIP_1$, constant round, and IND-CPA protocol for $\BQP$ with negligible completeness and soundness.

\begin{thm}
	\protoref{BlindBQP} has negligible completeness
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{Well, we'll pretend it's true...}
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{It sounds good, so it must be true.}
\end{proof}

\begin{thm}
	\protoref{BlindBQP} is IND-CPA
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{I have this gut feeling.}
\end{proof}

@@

\begin{thm}
	There is a way to compile a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	into a $\QPIP_0$ protocol with negl. completeness and soundness
\end{thm}
